\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-09 article.tex
Add gep example

\subsubsection{Implementing \mintinline{llvm}{gep} instructions}\label{impl-gep}
GEP instructions are used to perform address calculations for accessing elements in  structures or arrays. GEP instructions are particularly useful for efficiently addressing elements in complex data structures.

>>>>

\subsubsection{Implementing \mintinline{llvm}{gep} instructions}\label{impl-gep}
GEP instructions are used to perform address calculations for accessing elements in  structures or arrays. They are particularly useful for efficiently addressing elements in complex data structures. For example, code accessing fields like line 8 in Figure \ref{fig:vector.c}, would  translate to the snippet seen in Figure \ref{fig:vector.ll}.

\begin{figure}[H]
   \begin{minipage}{0.48\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{c}
typedef struct {
  int x;
  int y;
} vector;

void dot(vector *a, vector *b) {
  a->x += b->x;
  a->y += b->y;     // -------->
}

     \end{minted}
     \caption{Subfield access}\label{fig:vector.c}
   \end{minipage}
   \begin{minipage}{0.48\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{llvm}
; ...
%6 = getelementptr %struct.vector,
            %i8* %1, i64 0, i32 1
%7 = load i32, i32* %6
%8 = getelementptr %struct.vector,
            %i8* %0, i64 0, i32 1
%9 = load i32, i32* %8
%10 = add i32 %9, %7
store i32 %10, i32* %8
; ...
     \end{minted}
     \caption{\texttt{clang -O1 -S -emit-llvm}}\label{fig:vector.ll}
   \end{minipage}
\end{figure}
